Higher-Order unification for free!

### 2024-04-15 paper/main.tex
solve a todo

\paragraph{Example of \progBetaRH}
We give a second look at the opening example in \cref{sec:beta}.
\todo{this is a little more complex that the opening problem}
The problem is compiled into:
%
% make test ONLY=7003 TEX=tex
\printAlll
  {{{X,\lambda x.Y},
    {(X\appsep a),a}}}
  {{{A,\lambda x.B},
    {C,a}}}
  {{{Y,B,0},
    {X,A,0}}}
  {{{\llambda,,C,(A\appsep a)}}}

@@

The first unification problems is solved by the substitution
$\sigma = \{~A \mapsto \lambda x.B~\}$. The \linkbeta becomes
\linkbetaM{}{C}{((\lambda x.B) \appsep a)} whose \rhs can be $\beta$-reduced to
$B$. $B$ is in \llambda and is unified with $C$. The resolution of the second
unification problem
gives the final substitution $\sigma = \{~A \mapsto \lambda x.B ~;~ B \mapsto C ~;~ C
\mapsto a ~\}$ that is decompiled into $\rho = \{~ X \mapsto \lambda x.a ~;~ Y \mapsto
a ~\}$.

>>>>

\paragraph{Example of \progBetaRH}
We give a second look at the opening example in \cref{sec:beta}.
% \todo{this is a little more complex that the opening problem}
The problem is compiled into:
%
% make test ONLY=7003 TEX=tex
\printAlll
  {{{X,\lambda x.a},
    {(X\appsep a),a}}}
  {{{A,\lambda x.a},
    {B,a}}}
  {{{X,A,0}}}
  {{{\llambda,,B,(A\appsep a)}}}

@@

The first unification problem is solved with the substitution
$\sigma = \{~A \mapsto \lambda x.a~\}$. The \linkbeta becomes
\linkbetaM{}{B}{((\lambda x.a) \appsep a)} whose \rhs can be $\beta$-reduced to
$a$. $a$ is in \llambda and is unified with $B$. The resolution of the second
unification problem
confirm that $B$ equal $a$. The final substitution $\sigma = \{~A \mapsto \lambda x.a ~;~ B \mapsto a ~\}$ is decompiled into $\rho = \{~ X \mapsto \lambda x.a ~;~ Y \mapsto
a ~\}$.
